Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-09-01 main_paper.tex
Add sentence about CCF.

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not.

>>>>

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not. Furthermore, after analyzing higher-order properties
of procedures based on analytical bias correction relative to the usual undersmothing approach, \cite{CCF15} argue that explicit bias-correction
 coupled with an analytical adjustment to the standard errors ``yields confidence intervals 
with coverage that is accurate, or better, than the best possible undersmoothing approach'' \citep[p.~2]{CCF15}, 
and provide bandwidth choice procedures which are ``coverage-error optimal.''
